A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/Metatheory.tex
Script statistics update; appendix table style

\paragraph{Statistics of the Proof}
The proof script consists of 7683 lines of Abella code with a total of
51 definitions and 567 theorems.
Figure~\ref{fig:proof_statistics} briefly summarizes the contents of each file.
The files are linearly dependent due to limitations of Abella.

\begin{figure}[ht]
\centering\begin{tabular}{|c|c|c|l|}\hline
    File(s) & SLOC & \#Theorems & Description\\\hline
    olist.thm, nat.thm  &  309 & 56  & Basic data structures\\\hline
    typing.thm          &  238 & 5   & Declarative \& algorithmic system, debug examples\\\hline
    decl.thm            &  226 & 33  & Basic declarative properties\\\hline
    order.thm           &  235 & 27  & The $|\cdot|_\forall$ measure; decl. subtyping strengthening\\\hline
    alg.thm             &  655 & 72  & Basic algorithmic properties\\\hline
    trans.thm           &  628 & 53  & \makecell[l]{Worklist instantiation and declarative transfer\\
                            Lemmas~\ref{lem:insert}, \ref{lem:extract}}\\\hline
    declTyping.thm      &  944 & 72  & \makecell[l]{Non-overlapping declarative system \\
                            Lemmas~\ref{lem:inv_allR}, \ref{lem:inv_chkAll},
                                \ref{lem:inv_chkLam}, \ref{lem:subsumption}}\\\hline
    soundness.thm       & 1086 & 70  & Soundness theorem; aux. lemmas on transfer\\\hline
    depth.thm           &  206 & 14  & The $|\cdot|_\to$ measure; Lemma~\ref{lem:prune_inst}\\\hline
    dcl.thm             &  383 & 12  & Non-overlapping declarative worklist \\\hline
    completeness.thm    & 1075 & 61  &
                            Completeness theorem; aux. lemmas and relations\\\hline
    inst\_decidable.thm &  830 & 42  & Other worklist measures; Lemma~\ref{lemma:inst:decidable}\\\hline
    decidability.thm    &  885 & 50  & Decidability theorem and corollary\\\hline
    smallStep.thm       &  120 &  2  & The equivalence between big-step and small-step\\\hline
    \hline\emph{Total}               & 7700 & 567 & (51 definitions in total)\\\hline
\end{tabular}
\caption{Statistics for the proof scripts}
\label{fig:proof_statistics}
\end{figure}

>>>>

\paragraph{Statistics of the Proof}
The proof script consists of 7977 lines of Abella code with a total of
51 definitions and 596 theorems.
Figure~\ref{fig:proof_statistics} briefly summarizes the contents of each file.
The files are linearly dependent due to limitations of Abella.

\begin{figure}[ht]
\centering\begin{tabular}{|c|c|c|l|}\hline
    File(s) & SLOC & \#Theorems & Description\\\hline
    olist.thm, nat.thm  &  311 & 57  & Basic data structures\\\hline
    typing.thm          &  245 & 7   & Declarative \& algorithmic system, debug examples\\\hline
    decl.thm            &  226 & 33  & Basic declarative properties\\\hline
    order.thm           &  235 & 27  & The $|\cdot|_\forall$ measure; decl. subtyping strengthening\\\hline
    alg.thm             &  679 & 80  & Basic algorithmic properties\\\hline
    trans.thm           &  616 & 53  & \makecell[l]{Worklist instantiation and declarative transfer\\
                            Lemmas~\ref{lem:insert}, \ref{lem:extract}}\\\hline
    declTyping.thm      &  909 & 70  & \makecell[l]{Non-overlapping declarative system \\
                            Lemmas~\ref{lem:inv_allR}, \ref{lem:inv_chkAll},
                                \ref{lem:inv_chkLam}, \ref{lem:subsumption}}\\\hline
    soundness.thm       & 1107 & 78  & Soundness theorem; aux. lemmas on transfer\\\hline
    depth.thm           &  206 & 14  & The $|\cdot|_\to$ measure; Lemma~\ref{lem:prune_inst}\\\hline
    dcl.thm             &  380 & 12  & Non-overlapping declarative worklist \\\hline
    completeness.thm    & 1124 & 61  &
                            Completeness theorem; aux. lemmas and relations\\\hline
    inst\_decidable.thm &  837 & 45  & Other worklist measures; Lemma~\ref{lemma:inst:decidable}\\\hline
    decidability.thm    &  983 & 57  & Decidability theorem and corollary\\\hline
    smallStep.thm       &  119 &  2  & The equivalence between big-step and small-step\\\hline
    \hline\emph{Total}               & 7977 & 596 & (51 definitions in total)\\\hline
\end{tabular}
\caption{Statistics for the proof scripts}
\label{fig:proof_statistics}
\end{figure}
